Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-03-27 paper.tex
update

\appendix
\section{jets parameter variations}
\textcolor{red}{KY: Please also add a section (either in the Discussion
or Appendix) to discuss about the parameter variations.
I think the figures you showed me are very important
and informative.}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}
\raggedright
\caption{Jet parameters.}
\label{tablb-jet-parameters}
\begin{tabular}{@{}llllllll@{}}
\toprule[1pt]\midrule[0.3pt]
                  & A          & B          & C          & D          & E          & F          & G          \\ \midrule
$k_{B}T$ (MeV)    & 1.720      & 17.200     & 1.720      & 0.172      & 1.720      & 1.720      & 1.720      \\
$\rho$ (g/cm$^3$) & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-25}$ & $10^{-27}$ & $10^{-26}$ \\
$\beta\gamma$     & 1.2        & 0.6        & 0.6        & 0.6        & 0.6        & 0.6        & 0.3        \\ \midrule
\end{tabular}
\end{table*}

\begin{figure*}
  \includegraphics[width=\textwidth]{figures/fig__jet_parameters.png}
  \caption
   {
    Jets parameters variation around the fiducial run:\
    $\beta\gamma=1.2$ (left), $\beta\gamma=0.6$ (middle), and $\beta\gamma=0.3$ (right).
   }
  \label{fig__jet_parameters}
\end{figure*}

>>>>

\appendix
\section{jets parameter variations}

\textcolor{red}{KY: Please also add a section (either in the Discussion
or Appendix) to discuss about the parameter variations.
I think the figures you showed me are very important
and informative.}

In this section, we present the simulation results (Fig. \ref{fig__slice-compare})\
using exactly same parameters\
except for the density ($\rho$), temperature ($k_{B}T$),\
and four-velocity ($\beta\gamma$) within the jet source.\
The parameters of jet models, including the fiducial run (C),\
covered in this appendix are given in Table \ref{tablb-jet-parameters}.

Three points are worth highlighting:
\begin{itemize}
   \item Increase density only (F$\rightarrow$C$\rightarrow$E):\\
   The runs F, C, and E demonstrate that an increase in density,
   causes a rise in the intensity of the shocks driven into the atmosphere,\
   and makes the post-shocked region hotter,\
   as well as leads the bubbles to be more asymmetric about the disk.
   Since the jets with higher denisty are more likely to\
   break through the thin disk in a short time\
   and more difficult to be elongated by stratified atmosphere afterward.

   \item Increase velocity only (G$\rightarrow$C$\rightarrow$A):\\
   Increasing magnitude of velocity also gives the hotter and asymmetric bubbles as increasing density.
   The temperature of the bubbles caused by increasing velocity\
   is closely similar to that of increasing density when kinetic energy is fixed.\

   \item Increase thermal energy only (B$\rightarrow$C$\rightarrow$D):\\
   These demonstrates that increasing thermal energy cannot affect\
   the morphology of bubbles significantly
\end{itemize}

   This shows that the morphology/dynamic of bubbles is mainly determined by\
   a kinetic energy of a jet flow. Jets with higher kinetic energy are more likely to\
   break through the thin disk in a short time\
   and more difficult to be elongated by stratified atmosphere afterward.

\begin{table*}
\raggedright
\caption{The list of runs showing different injected jet parameters.\
         The fiducial run (C) has been pointed out by an asterisk in the list. }
\label{tablb-jet-parameters}
\begin{tabular}{@{}llllllll@{}}
\toprule[1pt]\midrule[0.3pt]
                  & A          & B          & C*         & D           & E          & F          & G          \\ \midrule
$k_{B}T$ (MeV)    & 1.720      & 0.172      & 1.720      & 17.200      & 1.720      & 1.720      & 1.720      \\
$\rho$ (g/cm$^3$) & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-26}$  & $10^{-25}$ & $10^{-27}$ & $10^{-26}$ \\
$\beta\gamma$     & 1.40       & 0.60       & 0.60       & 0.60        & 0.60       & 0.60       & 0.28       \\ \midrule
\end{tabular}
\end{table*}

%  A    G
% 1.4 0.28

%\begin{figure*}
%  \includegraphics[width=\textwidth]{figures/fig__jet_parameters.png}
%  \caption
%   {
%    Jets parameters variation around the fiducial run:\
%    $\beta\gamma=1.2$ (left), $\beta\gamma=0.6$ (middle), and $\beta\gamma=0.3$ (right).
%   }
%  \label{fig__jet_parameters}
%\end{figure*}
